Determination of Center of Rotation \\ in Computed Tomography

### 2017-07-22 seminar_cor/seminar_cor_haegele.tex
done with conclusion

\subsection{Image Acquisition in CT}
This subsection will briefly explain how images are typically aquired in CT.

@@

\subsubsection{Parallel Beam}
The simplest geometry in CT (from a mathematical point of view) is the parallel beam geometry.
Here all rays are parallel that are emitted from the same side of the object.
\Cref{subfig:parallelbeam} shows a schematic of this geometry with the resulting signal.
%
\begin{figure}[!h]
\centering
\subfloat[Parallel Beam]{\includegraphics[width=0.58\linewidth]{img/parallel_beam_geometry}%
\label{subfig:parallelbeam}}
\hfil
\subfloat[Fan Beam]{\includegraphics[width=0.4\linewidth, trim=0 -6cm 0 0]{img/fanbeamgeometry}%
\label{subfig:fanbeam}}
\caption{Parallel beam and fan beam geometry. 
In parallel beam the source moving perpendicular to the ray direction for sampling a 1-dimensional image (graph). 
In fan beam, rays are not perpendicular but instead emmited in fan blade form. 
$\gamma$ is the rotation angle at which the signal is obtained. 
Figures from~\cite{Buzug2008_chap3,Buzug2008_chap4}}
\label{fig:parallalandfanbeam}
\end{figure}

@@

\subsubsection{Fan Beam}
A more practical geometry is the fan beam, in which a source emits a flat beam that extends to the sides (like a fan blade). 
\Cref{subfig:fanbeam} shows a schematic of this geometry.
Here the projection for a single rotation angle can be obtained at once. 
The geometry can be defined by the COR it rotates around, the offset of the source to the COR and its aperture angle.
In clinical practise curved detector rays are used, as shown in \cref{subfig:fanbeam}, to get constant aperture angle steps for each detector cell.
%
\begin{figure}[!h]
\centering
\subfloat[]{\includegraphics[width=0.43\linewidth]{eps/rebinning.eps}%
\label{subfig:rebinning1}}
\hfil
\subfloat[]{\includegraphics[width=0.51\linewidth]{eps/rebinning_geo.eps}%
\label{subfig:rebinning2}}
\caption{
On the left a schematic is shown with two fan beams with aperture angle $\varphi$ at different rotation angles.
It can be sen that the outer rays of the two are parallel.
The maximum distance of two parallel beams is limited by $\varphi$, and the maximum rotation angle $\theta$ at which two
parallel rays can be obtained is given by $\theta = \psi_{min}+\psi_{max}$ which are the angles from central to outer rays.
On the right a schematic is shown that points out the correspondence between fan and parallel beam geometry.
It can be seen that for the red ray which is the ray at rotation angle $\theta$ with deviation angle $\psi$ from the central ray, there exists an angle $\gamma$ in parallel beam geometry so that it is perpendicular to the $r$-axis (i.e. parallel beam detector).
Figures from~\cite{Buzug2008_chap7}
}
\label{fig:rebinning}
\end{figure}
%

@@

\subsection{Reconstruction}
This subsection will explain the process of reconstructing an image from the projections obtained in CT.
Only the 2D case will be explained as it is relevant for understanding the COR determination techniques later on.
Also this subsection will only cover Fourier based reconstruction, especially filtered back projection.

@@

\subsubsection{High Density Feature}
Crawford~et~al.~\cite{crawford1988} presented an approach for finding the COR in which they used two $180^\circ$ opposing projections of a distinct high density feature.
When locating this feature in the two projections, the COR can be calculated as the sum of the detector coordinates of the feature divided by two.
This becomes clear when thinking about the feature being offset from the COR by $\delta$ in projection $p_1$.
The corresponding position of the feature in projection $p_2$ will then be on the opposite side of the COR, offset by $-\delta$ from the COR. \Cref{fig:highdenistyfeature} illustrates this concept.
%
\begin{figure}[!h]
\centering
\subfloat[phantom]{\includegraphics[width=0.32\linewidth]{img/highdensity_inv.png}}
\hfil
\subfloat[sinogram]{\includegraphics[width=0.65\linewidth]{img/highdensityradon_degrees_feature_centerline_horiz.png}}
\caption{
A phantom with a high density feature is shown on the left side.
In corresponding sinogram on the right, the sinusodial trace of the feature can be observed.
The dotted line indicates the COR in the sinogram.
It can be seen that the feature locations in $180^\circ$ opposing projections have the same distance to the COR.  
}
\label{fig:highdenistyfeature}
\end{figure}
%

@@

\subsubsection{Center of Mass}
Azevedo~et~al.~\cite{azevedo90} proposed a more generally applicable algorithm, in which they replaced the high density feature from \cite{crawford1988} with the center of mass.
The center of mass of the original signal is a point $(\overline{x},\overline{y}$) which's coordinates can be calculated as follows (calculation of $\overline{y}$ analogous to $\overline{x}$).
%
\begin{equation}
\overline{x} = \frac{
\int_{-\infty}^{\infty}\int_{-\infty}^{\infty}x\;f(x,y)\;dx\;dy
}
{
\int_{-\infty}^{\infty}\int_{-\infty}^{\infty}f(x,y)\;dx\;dy
}
\end{equation}
%
As the center of mass of the original signal $f(x,y)$ is projected onto the projection center of mass in parallel beam geometry, it can be used as a reference feature.
The projection center of mass is dependent on the projection angle and can be calculated as follows.
%
\begin{equation}
\overline{r_\tau}(\gamma) = \frac{
\int_{-\infty}^{\infty}r\;R_\tau(r,\gamma)\;dr
}
{
\int_{-\infty}^{\infty}R_\tau(r,\gamma)\;dr
}
=
\frac{
\int_{-\infty}^{\infty}r\;R(r-\tau,\gamma)\;dr
}
{
\int_{-\infty}^{\infty}R_(r-\tau,\gamma)\;dr
}
\end{equation}
%
where $R_\tau(r,\gamma)$ is the radon transform with COR offset by~$\tau$ (\cref{eq:radonoffset}).
The previous equation can be simplified to the following.
%
\begin{equation}
\label{eq:projection_centerofmass}
\overline{r_\tau}(\gamma) = \tau + \overline{r}(\gamma) = \tau + \overline{x}\;cos(\gamma) + \overline{y}\;sin(\gamma)
\end{equation}
%
Using linear regression (least squares) the parameters $\tau$, $\overline{x}$ and $\overline{y}$ can be approximated from the matrix notation of \cref{eq:projection_centerofmass}.
%
\begin{equation}
\begin{pmatrix}
1 & cos(\gamma_1) & sin(\gamma_1) \\
\vdots & \vdots & \vdots \\
1 & cos(\gamma_n) & sin(\gamma_n) 
\end{pmatrix}
\cdot
\begin{pmatrix}
\tau \\
\overline{x} \\
\overline{y}
\end{pmatrix}
=
\begin{pmatrix}
\overline{r_\tau}(\gamma_1) \\
\vdots \\
\overline{r_\tau}(\gamma_n)
\end{pmatrix}
\end{equation}
%
Even though $\overline{x}$ and $\overline{y}$ are not needed for a correct reconstruction, it is a neat bonus.

@@

\subsubsection{Cross-Correlation}
Yang et al.~\cite{Yang2011} proposed another sinogram based method for COR determination using image cross-correllation.
Given a sinogram in a prallel beam geometry over $360^\circ$ (which can also be obtained by rebinning a fan-beam sinogram), the sinogram is divided in half so that both halfs cover a $180^\circ$ range.
As the information in both sub sinograms is redundant in that way that they are mirror images of each other,
flipping one of them will result in two sinograms over $180^\circ$ with identical information.
%
\begin{equation}
R(r,\gamma)^{[0,\pi]} = R(-r,\gamma)^{[\pi,2\pi]}
\end{equation}
%
A shift of COR, as explained in the beginning of \cref{sec:cordetermination}, results in a shift of the sinogram along the $r$-axis (see~\cref{eq:radonoffset}).
Thus, the two sub sinograms are identical under this shift.
%
\begin{equation}
R_\tau(r+\tau,\gamma)^{[0,\pi]} = R_\tau(-(r+\tau),\gamma)^{[\pi,2\pi]}
\end{equation}
%
Using the 1D cross correlation of the two sinograms along the $r$-axis, the shift can be determined as follows.
%
\begin{equation}
2\tau = \underset{r}{arg\,max}\quad R_\tau(r,\gamma)^{[0,\pi]} \star R_\tau(-r,\gamma)^{[\pi,2\pi]}
\end{equation}
%
The authors~\cite{Yang2011} provided evidence that their algorithm is robust against Gaussian noise even for large variance values.
They also stated that their algorithm can be used for 3D CT with cone beam geometry when using the central slice (see \cref{sssec:conebeam}).
As locating the central slice is not trivial and depends on calibration as well, it was shown that the algorithm still performs well for sinograms that slightly deviate from that of the central slice.

\subsection{Reconstruction Based Methods}
Reconstruction based methods, as opposed to sinogram based methods, use an iterative approach to finding the COR.
The individual steps of an iterative algorithm are:
\begin{enumerate}
\item reconstruct image with COR $\tau_i$
\item generate a score for the reconstructed image that indicates the quality of the reconstruction, and thus the correctness of $\tau_i$
\item repeat for different $\tau_i$
\item select $\tau_i$ with best score as correct COR
\end{enumerate}
This process is of course very time consuming due to the repeating reconstruction step, but is not dependent on specific CT geometries.
The crucial part of this algorithm is the generation of a score, which requires an image metric $Q(\tilde{f})$ to assess the quality of the reconstructed image $\tilde{f}$.
In the following two different metrics are introduced.

\subsubsection{Integral of Negativity}
As proposed by Donath et~al.~\cite{donath2006} the integral of negativity can be leveraged to build an image metric $Q_{IN}$.
%
\begin{align}
Q_{IN}(\tilde{f}) &= -\frac{1}{m_0}\;\int_{-\infty}^{\infty}\int_{-\infty}^{\infty}\varepsilon(-\tilde{f}(x,y))\,\tilde{f}(x,y)\;dx\,dy.
\\
m_0 &= \int_{-\infty}^{\infty}\int_{-\infty}^{\infty}f(x,y)\;dx\,dy = \int_{-\infty}^{\infty} R(r,\gamma_0)\;dr
\\
\varepsilon(a) &= \bigg\{
\begin{matrix}
1: & a \geq 0 \\
0: & else
\end{matrix}\quad \text{(Heaviside function)} 
\end{align}
%
$Q_{IN}$ is calculated as the ratio of the integral of negativity of the reconstructed image to the zeroth order moment $m_0$ (total mass) of the original signal. 
Fortunately the original image does not need to be known in order to calculate $m_0$, it is the integral of along the $r$-axis of any projection of the sinogram.

@@

\subsubsection{Histogram Entropy}
As pointed out by Donath et~al.~\cite{donath2006}, the metric $Q_{IN}$ can only be used for non-negative object functions.
Therefore they provided another metric based on the histogram entropy that is also applicable when negative attenuation coefficients are present (which can occur when samples are recorded in a surrounding medium e.g. water \cite{donath2006}).
They defined a metric $Q_H$ as follows.
%
\begin{align}
Q_H(\tilde{f}) &= \frac{H}{H_{max}} 
\\
H &= -\int_{-\infty}^{\infty}p(g)\,log_2(h\,p(g))\;dg
\end{align}
%
Here the metric is build by normalizing the entropy $H$ by the maximum entropy $H_{max}$.
$H$ is a continous version of the discrete entropy for gray-level images, where $p(g)$ is an estimate probability density function for continous gray levels $g$ and $h$ describes the density resolution.

@@

\section{Conclusion}
The conclusion goes here.

@@

\appendices
\section{}

>>>>

\subsection{Image Acquisition in CT}\label{ssec:imageacquisition}
This subsection will briefly explain how images are typically aquired in CT.

@@

\subsubsection{Parallel Beam}\label{sssec:parallelbeam}
The simplest geometry in CT (from a mathematical point of view) is the parallel beam geometry.
Here all rays are parallel that are emitted from the same side of the object.
\Cref{subfig:parallelbeam} shows a schematic of this geometry with the resulting signal.
%
\begin{figure}[!h]
\centering
\subfloat[Parallel Beam]{\includegraphics[width=0.58\linewidth]{img/parallel_beam_geometry}%
\label{subfig:parallelbeam}}
\hfil
\subfloat[Fan Beam]{\includegraphics[width=0.4\linewidth, trim=0 -6cm 0 0]{img/fanbeamgeometry}%
\label{subfig:fanbeam}}
\caption{Parallel beam and fan beam geometry. 
In parallel beam the source moving perpendicular to the ray direction for sampling a 1-dimensional image (graph). 
In fan beam, rays are not perpendicular but instead emmited in fan blade form. 
$\gamma$ is the rotation angle at which the signal is obtained. 
Figures from~\cite{Buzug2008_chap3,Buzug2008_chap4}}
\label{fig:parallalandfanbeam}
\end{figure}

@@

\subsubsection{Fan Beam}\label{sssec:fanbeam}
A more practical geometry is the fan beam, in which a source emits a flat beam that extends to the sides (like a fan blade). 
\Cref{subfig:fanbeam} shows a schematic of this geometry.
Here the projection for a single rotation angle can be obtained at once. 
The geometry can be defined by the COR it rotates around, the offset of the source to the COR and its aperture angle.
In clinical practise curved detector rays are used, as shown in \cref{subfig:fanbeam}, to get constant aperture angle steps for each detector cell.
%
\begin{figure}[!h]
\centering
\subfloat[]{\includegraphics[width=0.43\linewidth]{eps/rebinning.eps}%
\label{subfig:rebinning1}}
\hfil
\subfloat[]{\includegraphics[width=0.51\linewidth]{eps/rebinning_geo.eps}%
\label{subfig:rebinning2}}
\caption{
On the left a schematic is shown with two fan beams with aperture angle $\varphi$ at different rotation angles.
It can be sen that the outer rays of the two are parallel.
The maximum distance of two parallel beams is limited by $\varphi$, and the maximum rotation angle $\theta$ at which two
parallel rays can be obtained is given by $\theta = \psi_{min}+\psi_{max}$ which are the angles from central to outer rays.
On the right a schematic is shown that points out the correspondence between fan and parallel beam geometry.
It can be seen that for the red ray which is the ray at rotation angle $\theta$ with deviation angle $\psi$ from the central ray, there exists an angle $\gamma$ in parallel beam geometry so that it is perpendicular to the $r$-axis (i.e. parallel beam detector).
Figures from~\cite{Buzug2008_chap7}
}
\label{fig:rebinning}
\end{figure}
%

@@

\subsection{Reconstruction}\label{ssec:reconstruction}
This subsection will explain the process of reconstructing an image from the projections obtained in CT.
Only the 2D case will be explained as it is relevant for understanding the COR determination techniques later on.
Also this subsection will only cover Fourier based reconstruction, especially filtered back projection.

@@

\subsubsection{High Density Feature}\label{sssec:highdensityfeature}
Crawford~et~al.~\cite{crawford1988} presented an approach for finding the COR in which they used two $180^\circ$ opposing projections of a distinct high density feature.
When locating this feature in the two projections, the COR can be calculated as the sum of the detector coordinates of the feature divided by two.
This becomes clear when thinking about the feature being offset from the COR by $\delta$ in projection $p_1$.
The corresponding position of the feature in projection $p_2$ will then be on the opposite side of the COR, offset by $-\delta$ from the COR. \Cref{fig:highdenistyfeature} illustrates this concept.
%
\begin{figure}[!h]
\centering
\subfloat[phantom]{\includegraphics[width=0.32\linewidth]{img/highdensity_inv.png}}
\hfil
\subfloat[sinogram]{\includegraphics[width=0.65\linewidth]{img/highdensityradon_degrees_feature_centerline_horiz.png}}
\caption{
A phantom with a high density feature is shown on the left side.
In corresponding sinogram on the right, the sinusodial trace of the feature can be observed.
The dotted line indicates the COR in the sinogram.
It can be seen that the feature locations in $180^\circ$ opposing projections have the same distance to the COR.  
}
\label{fig:highdenistyfeature}
\end{figure}
%

@@

\subsubsection{Center of Mass}\label{sssec:centerofmass}
Azevedo~et~al.~\cite{azevedo90} proposed a more generally applicable algorithm, in which they replaced the high density feature from \cite{crawford1988} with the center of mass.
The center of mass of the original signal is a point $(\overline{x},\overline{y}$) which's coordinates can be calculated as follows (calculation of $\overline{y}$ analogous to $\overline{x}$).
%
\begin{equation}
\overline{x} = \frac{
\int_{-\infty}^{\infty}\int_{-\infty}^{\infty}x\;f(x,y)\;dx\;dy
}
{
\int_{-\infty}^{\infty}\int_{-\infty}^{\infty}f(x,y)\;dx\;dy
}
\end{equation}
%
As the center of mass of the original signal $f(x,y)$ is projected onto the projection center of mass in parallel beam geometry, it can be used as a reference feature.
The projection center of mass is dependent on the projection angle and can be calculated as follows.
%
\begin{equation}
\overline{r_\tau}(\gamma) = \frac{
\int_{-\infty}^{\infty}r\;R_\tau(r,\gamma)\;dr
}
{
\int_{-\infty}^{\infty}R_\tau(r,\gamma)\;dr
}
=
\frac{
\int_{-\infty}^{\infty}r\;R(r-\tau,\gamma)\;dr
}
{
\int_{-\infty}^{\infty}R_(r-\tau,\gamma)\;dr
}
\end{equation}
%
where $R_\tau(r,\gamma)$ is the radon transform with COR offset by~$\tau$ (\cref{eq:radonoffset}).
The previous equation can be simplified to the following.
%
\begin{equation}
\label{eq:projection_centerofmass}
\overline{r_\tau}(\gamma) = \tau + \overline{r}(\gamma) = \tau + \overline{x}\;cos(\gamma) + \overline{y}\;sin(\gamma)
\end{equation}
%
Using linear regression (least squares) the parameters $\tau$, $\overline{x}$ and $\overline{y}$ can be approximated from the matrix notation of \cref{eq:projection_centerofmass}.
%
\begin{equation}
\begin{pmatrix}
1 & cos(\gamma_1) & sin(\gamma_1) \\
\vdots & \vdots & \vdots \\
1 & cos(\gamma_n) & sin(\gamma_n) 
\end{pmatrix}
\cdot
\begin{pmatrix}
\tau \\
\overline{x} \\
\overline{y}
\end{pmatrix}
=
\begin{pmatrix}
\overline{r_\tau}(\gamma_1) \\
\vdots \\
\overline{r_\tau}(\gamma_n)
\end{pmatrix}
\end{equation}
%
Even though $\overline{x}$ and $\overline{y}$ are not needed for a correct reconstruction, it is a neat bonus.

@@

\subsubsection{Cross-Correlation}\label{sssec:crosscorrelation}
Yang et al.~\cite{Yang2011} proposed another sinogram based method for COR determination using image cross-correllation.
Given a sinogram in a prallel beam geometry over $360^\circ$ (which can also be obtained by rebinning a fan-beam sinogram), the sinogram is divided in half so that both halfs cover a $180^\circ$ range.
As the information in both sub sinograms is redundant in that way that they are mirror images of each other,
flipping one of them will result in two sinograms over $180^\circ$ with identical information.
%
\begin{equation}
R(r,\gamma)^{[0,\pi]} = R(-r,\gamma)^{[\pi,2\pi]}
\end{equation}
%
A shift of COR, as explained in the beginning of \cref{sec:cordetermination}, results in a shift of the sinogram along the $r$-axis (see~\cref{eq:radonoffset}).
Thus, the two sub sinograms are identical under this shift.
%
\begin{equation}
R_\tau(r+\tau,\gamma)^{[0,\pi]} = R_\tau(-(r+\tau),\gamma)^{[\pi,2\pi]}
\end{equation}
%
Using the 1D cross correlation of the two sinograms along the $r$-axis, the shift can be determined as follows.
%
\begin{equation}
2\tau = \underset{r}{arg\,max}\quad R_\tau(r,\gamma)^{[0,\pi]} \star R_\tau(-r,\gamma)^{[\pi,2\pi]}
\end{equation}
%
The authors~\cite{Yang2011} provided evidence that their algorithm is robust against Gaussian noise even for large variance values.
They also stated that their algorithm can be used for 3D CT with cone beam geometry when using the central slice (see \cref{sssec:conebeam}).
As locating the central slice is not trivial and depends on calibration as well, it was shown that the algorithm still performs well for sinograms that slightly deviate from that of the central slice.

\subsection{Reconstruction Based Methods}\label{ssec:reconstructionbasedmethods}
Reconstruction based methods, as opposed to sinogram based methods, use an iterative approach to finding the COR.
The individual steps of an iterative algorithm are:
\begin{enumerate}
\item reconstruct image with COR $\tau_i$
\item generate a score for the reconstructed image that indicates the quality of the reconstruction, and thus the correctness of $\tau_i$
\item repeat for different $\tau_i$
\item select $\tau_i$ with best score as correct COR
\end{enumerate}
This process is of course very time consuming due to the repeating reconstruction step, but is not dependent on specific CT geometries.
The crucial part of this algorithm is the generation of a score, which requires an image metric $Q(\tilde{f})$ to assess the quality of the reconstructed image $\tilde{f}$.
In the following two different metrics are introduced.

\subsubsection{Integral of Negativity}\label{sssec:qin}
As proposed by Donath et~al.~\cite{donath2006} the integral of negativity can be leveraged to build an image metric $Q_{IN}$.
%
\begin{align}
Q_{IN}(\tilde{f}) &= -\frac{1}{m_0}\;\int_{-\infty}^{\infty}\int_{-\infty}^{\infty}\varepsilon(-\tilde{f}(x,y))\,\tilde{f}(x,y)\;dx\,dy.
\\
m_0 &= \int_{-\infty}^{\infty}\int_{-\infty}^{\infty}f(x,y)\;dx\,dy = \int_{-\infty}^{\infty} R(r,\gamma_0)\;dr
\\
\varepsilon(a) &= \bigg\{
\begin{matrix}
1: & a \geq 0 \\
0: & else
\end{matrix}\quad \text{(Heaviside function)} 
\end{align}
%
$Q_{IN}$ is calculated as the ratio of the integral of negativity of the reconstructed image to the zeroth order moment $m_0$ (total mass) of the original signal. 
Fortunately the original image does not need to be known in order to calculate $m_0$, it is the integral of along the $r$-axis of any projection of the sinogram.

@@

\subsubsection{Histogram Entropy}\label{sssec:qh}
As pointed out by Donath et~al.~\cite{donath2006}, the metric $Q_{IN}$ can only be used for non-negative object functions.
Therefore they provided another metric based on the histogram entropy that is also applicable when negative attenuation coefficients are present (which can occur when samples are recorded in a surrounding medium e.g. water \cite{donath2006}).
They defined a metric $Q_H$ as follows.
%
\begin{align}
Q_H(\tilde{f}) &= \frac{H}{H_{max}} 
\\
H &= -\int_{-\infty}^{\infty}p(g)\,log_2(h\,p(g))\;dg
\end{align}
%
Here the metric is build by normalizing the entropy $H$ by the maximum entropy $H_{max}$.
$H$ is a continous version of the discrete entropy for gray-level images, where $p(g)$ is an estimate probability density function for continous gray levels $g$ and $h$ describes the density resolution.

@@

\section{Conclusion}
In this paper about the determination of the COR in CT, a brief introduction was given about image acquisition in CT in the beginning~(\cref{ssec:imageacquisition}).
Several CT geometries were introduced; 
the parallel beam geometry~(\cref{sssec:parallelbeam}) which is mathematically described by the Radon transform and which most of the COR determination algorithms assume;
the fan beam geometry (\cref{sssec:fanbeam}) which is more common and can be transormed to a parallel beam geometry;
and the cone beam geometry (\cref{sssec:conebeam}) which, in contrast to the former, is a 3D geometry.
In the last part of the introduction to CT imaging, the reconstruction was discussed (\cref{ssec:reconstruction}) in which the Fourier slice theorem was explained as well as the filtered back projection (\cref{sssec:fbp}) as a representative reconstruction algorithm.

In the following section the key topic of this paper was adressed.
Firstly the problem of inaccurate or wrong COR assumption for reconstruction was explained (\cref{sec:cordetermination}) which is the image degradation due to artifacts.
Afterwards the different methdods for COR determination found in the literature were presented which can be classified into sinogram based methods and reconstruction based methods.

The sinogram based methods comprise the high density feature tracing method (\cref{sssec:highdensityfeature}), in which a pin phantom can be used to create a distinct sinusodial trace in the sinogram from which the actual COR can be deduced;
the center of mass method (\cref{sssec:centerofmass}) which is also applicable without the use of a special phantom as it uses the objects center of mass as a tracing point;
and the cross-correlation method (\cref{sssec:crosscorrelation}) which leverages the redundant information in the upper and lower half of a sinogram over $360^\circ$.

In the section of reconstruction based methods a basic iterative algorithm was introduced (\cref{ssec:reconstructionbasedmethods}) which uses uses an image metric to judge the quality of a reconstructed image.
Following that, two image metrics were presented that could be used in the algorithm, which are the integral of negativity metric (\cref{sssec:qin}) and the histogram entropy metric (\cref{sssec:qh}).

@@

%\appendices
%\section{}
